Attempting to write a full model

### 2016-09-17 R/misc/fullModel.rmd
tweais

            list(c(dS, dI, dSS, dSI, dII), 
            		 ##tot_I = tot_I, mean_V = tot_V/tot_I
            		 mort.SI.out)
        })
    }
}

@@

full_model_rcpp <- function(t, yini, parameters){
	return(list(unlist(g2(t, yini, parameters))))
}

pp <- expand(HIVpars.mean)

tvec <- seq(1, 30, 0.5)

r_rcpp <- lsoda(unlist(yini2), func = full_model_rcpp, parms = pp, times = tvec)
N_rcpp <- with(expand(HIVpars.mean),{
        S <- r_rcpp[,2:(1+n.risk)]
        I <- apply(r_rcpp[,(2+n.risk):(1+n.risk+n.risk*n.alpha)], 1, function(x) colSums2(x, n.alpha))
        return(S + t(I))
})

@@

microbenchmark(
tmpa = c(unname(g2(0, unlist(yini4), expand(HIVpars.mean))$dSI)),
tmpb = c(unname(model2(expand(HIVpars.mean), infection = TRUE, mortality = TRUE)(0, unlist(yini4), expand(HIVpars.mean))[[1]][76:264]))
)
##1:3, 4:66. 67:75, 76:264
##-c(1:264)
all.equal(tmpa, tmpb)
plot(tmpa)
plot(tmpb)
```

>>>>

            list(c(dS, dI, dSS, dSI, dII), tot_I = tot_I, mean_V = tot_V/tot_I)
        })
    }
}

@@

full_model_rcpp <- function(t, yini, parameters){
	return(list(unlist(rcppFull(t, yini, parameters))))
}

parstmp <- transform(HIVpars.mean, n.risk = 6, r.risk = c(0.8, 0.9, 1, 1, 1.1, 1.2), p.risk = c(0.15, 0.15, 0.2 , 0.2, 0.15, 0.15))

yini2 <- calc_yini_full(parstmp)

pp <- expand(parstmp)

tvec <- seq(1, 4000, 1)

system.time(r_rcpp <- rk(unlist(yini2), func = full_model_rcpp, parms = pp, times = tvec))
N_rcpp <- with(expand(HIVpars.mean),{
        S <- r_rcpp[,2:(1+n.risk)]
        I <- apply(r_rcpp[,(2+n.risk):(1+n.risk+n.risk*n.alpha)], 1, function(x) colSums2(x, n.alpha))
        return(S + t(I))
})

@@

tmpa = c(unname(rcppPartner(0, unlist(yini4), expand(HIVpars.mean))$dII))

tmpb = c(unname(model2(expand(HIVpars.mean))(0, unlist(yini4), expand(HIVpars.mean))[[1]][-c(1:264)]))

##1:3, 4:66. 67:75, 76:264
##-c(1:264)
all.equal(tmpa, tmpb)
plot(tmpa)
plot(tmpb)
```
